Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-06-21 paper/paper.tex
minor changes in intro

%\vspace{-1ex}
%noitemsep,
\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
\item \emph{Test transplantation} leverages diversity of test
  cases. It evaluates the effects that running test files from a given
  engine have in detecting bugs in other engines. The intuition is
  that developers design test cases with different objectives in
  mind. As such, replaying these tests in different engines could
  reveal unanticipated problems.

\item \emph{Cross-engine differential testing} leverages diversity of
  engine implementations. More precisely, it fuzzes existing test
  inputs~\cite{fuzz-testing-history} and then compares the output
  produced by different engines using a differential oracle. The
  intuition is that similar inputs to those already tested may reveal
  problems.
\end{itemize}

Our study measures the ability of these techniques in finding bugs and
the impact of false positives, which can arise in both testing
scenarios, on the practicality of the approach.

>>>>

%\vspace{-1ex}
%noitemsep,
\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
\item \emph{Test transplantation} leverages diversity of test
  cases. This technique evaluates the effect of running test files
  written for a given engine in other engines. The intuition is that
  developers design test cases with different objectives in mind. As
  such, replaying these tests in different engines could reveal
  unanticipated problems.

\item \emph{Cross-engine differential testing} leverages diversity of
  engine implementations. This technique fuzzes existing test
  inputs~\cite{fuzz-testing-history} and then compares the output
  produced by different engines.\Comment{ using a differential
    oracle.} The intuition is that interesting inputs can be created
  from existing inputs and multiple engines can be used to address the
  lack of oracles.
\end{itemize}

Our study measures the ability of these techniques in finding bugs and
the impact of false positives, which can arise in both testing
scenarios, on their practicality.
